Think deep for reef resilience

### 2025-08-14 paper/paper_draft.qmd
Additional small details for Source:Sink connectivity ratio

The ratio of source-to-sink connectivity for a target reef is calculated using @eq-so-to-si,
and represents the strength of the reef's outgoing larval flow relative to it's incoming
larval flow. Incoming connections in this calculation, do not directly represent the larval
supply gained as the population from which connections are coming from is not represented. A
source-to-sink ratio greater than 1 (a value greater than 0 on a log scale) indicates a reef
has greater outgoing than incoming larval flow.

>>>>

The ratio of source-to-sink connectivity ($O:I$) for a target reef is calculated using
@eq-so-to-si, and represents the strength of the reef's outgoing larval flow relative to
it's incoming larval flow. If a reef has no incoming connections, the $O:I$ equals the
$\frac{S_O}{N_O}$ value. Incoming connections in this calculation, do not directly represent
the larval supply gained as the population from which connections are coming from is not
represented. A source-to-sink ratio greater than 1 (a value greater than 0 on a log scale)
indicates a reef has greater outgoing than incoming larval flow.
